% !TEX TS-program = LuaLaTeX

\documentclass[12pt]{article}

\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{scrextend}
\usepackage{etaremune}
\usepackage{mathptmx}
%\usepackage{tgtermes}
\usepackage{color}
\usepackage{etaremune}

% use http link for email
\usepackage[colorlinks = true,
          allcolors = PineGreen]{hyperref}            
            %
            
%allow formula formatting
\usepackage{amsmath}
%\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
\usepackage{comment}

%title positon
\usepackage{titling} %fix title
\setlength{\droptitle}{-6em}   % Move up the title 

%change section title font size
\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\fontsize{12}{15}}{\thesection}{1em}{}[{\titlerule[0.5pt]}]
  
\titleformat{\subsection}
  {\normalfont\fontsize{12}{13}}{\thesection}{1em}{}

% change page margin and cancel identation
\usepackage[top=0.6in, bottom=0.8in, left=0.5in, right=0.5in]{geometry} 
\setlength{\parindent}{0pt}


%allow modifying section titles 
\usepackage[dvipsnames]{xcolor}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0in}
  }
}{
  \end{list}
}

\begin{document}
\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}%
\begin{center}
	\textbf{
			{\huge I}{\Large SABEL} \hspace{-0.1em} 
			{\huge R}{\Large OSE} \hspace{-0.1em} 
			{\huge F}{\Large ULCHER}}\\
\end{center}
\begin{minipage}[t]{0.5\linewidth}
\begin{flushleft}
	\MYhref[black]{mailto:isabel_fulcher@hms.harvard.edu}{isabel\_fulcher@hms.harvard.edu} \\
	\MYhref[black]{http://orcid.org/0000-0002-1209-824X}{ORCID: 0000-0002-1209-824X} 
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.5\linewidth} 
\begin{flushright}  
	%\vspace*{1mm} 
	{\LARGE
		\href[pdfnewwindow=true]{http://isabelfulcher.github.io}{\faGlobe} \href{https://github.com/isabelfulcher}{\faGithub}  \href{https://scholar.google.com/citations?user=Pb7FyDkAAAAJ&hl=en}{\faGoogle}  \href{mailto:isabel_fulcher@hms.harvard.edu}{\faEnvelope }   \par
	}
\end{flushright}  
\end{minipage}

\section*{\textbf{{\large E}DUCATION}}

\textbf{Harvard University} \hfill \hfill \textbf{Cambridge, MA}

Doctor of Philosophy, Biostatistics \hfill \hfill March 2019 
\begin{addmargin}[1em]{2em} \small{Dissertation Advisor: Eric Tchetgen Tchetgen} \\
\small{Dissertation Title: ``Statistical Inference for Causal Mechanisms: Mediation and Interference'' \\} \end{addmargin} 

\textbf{Harvard University} \hfill \hfill \textbf{Cambridge, MA}

Masters of Arts, Biostatistics \hfill \hfill May 2016

\vspace{.5cm}

\textbf{McGill University} \hfill \hfill \textbf{Montreal, QC} \\
Bachelor of Arts and Science, Mathematics and Anthropology  \hfill \hfill May 2012 


%% Research Experience
\section*{\textbf{{\large A}CADEMIC {\large A}PPOINTMENTS }}

\textbf{Harvard Data Science Initiative \hfill \hfill Cambridge, MA} \\
\textit{Postdoctoral Fellow}  \hfill \hfill September 2019 -- Current \\

\textbf{Department of Global Health and Social Medicine, Harvard Medical School \hfill \hfill Boston, MA} \\
\textit{Postdoctoral Fellow} \hfill \hfill January 2019 -- August 2019 \\
Advisers: Bethany Hedt-Gauthier and Eric Tchetgen Tchetgen 

% Peer-Reviewed Publications
\section*{\textbf{{\large P}{EER}-{\large R}{EVIEWED} {\large P}{UBLICATIONS}}}

\subsection*{\textbf{FIRST AUTHOR}}

\begin{enumerate}

\setcounter{enumi}{0}
	
	% PP COVID paper 
	
	% Causal paper - BHG
	
	% Seb paper
	
	% LQAS paper
	
	\item \textbf{Fulcher, I. R.}$^{*}$, Neill, S.$^{*}$, Bhardwa, S., Goldberg, A.B., Janiak, E. (2020). State and federal abortion restrictions increase risk of COVID-19 exposure by mandating unnecessary clinic visits. \textit{In Press} at Contraception. 
	
	\item \textbf{Fulcher, I. R.}, Nelson, A., Tibaijuka, J., Seif, S., Lilienfeld, S., Abdalla O., Beckmann, N., Layer, E., Hedt-Gauthier, B., \& Hoffman, R. (2020). Improving health facility delivery rates in Zanzibar, Tanzania through a large-scale digital community health volunteer program: A process evaluation. \textit{In Press} at Health Policy \& Planning. 
	
	\item \textbf{Fulcher, I. R.}, Shpitser, I., \& Tchetgen Tchetgen, E. J. (2020). Robust inference on population indirect causal effects: the generalized front-door criterion. Journal of the Royal Statistical Society Series B. DOI: 10.1111/rssb.12345
	
	\item \textbf{Fulcher, I. R.}, Hedt, K., Marealle, S., Abdalla O., Tibaijuka, J., Hoffman, R., Layer, E., Mitchell, M., \& Hedt-Gauthier, B. (2020). Errors in estimated gestational ages reduce the likelihood of health facility deliveries: results from an observational cohort study in Zanzibar. BMC Health Services Research, 20(1).

	\item \textbf{Fulcher, I. R.}, Shi, X., \& Tchetgen Tchetgen, E. J. (2019). Estimation of natural indirect effects robust to unmeasured confounding and mediator measurement error. Epidemiology, 30(6), 825-834.
	
	\item \textbf{Fulcher, I. R.}, Tchetgen Tchetgen E. J., \& Williams, P. L. (2017). Mediation analysis for censored survival data under an accelerated failure time model.  Epidemiology, 28(5), 660-666. 
	
\end{enumerate}

\subsection*{\textbf{CO-AUTHORED}}
\begin{enumerate} 
	\setcounter{enumi}{5}
	
	% Planned Parenthood - Opioid
	
	% Planned Parenthood - Minors cost
	
	% UPMC 
		
	\item Tchetgen Tchetgen, E. J., \textbf{Fulcher, I. R.}, \& Shpitser, I. (2020). Auto-g-computation of causal effects on a network. \textit{In Press} at Journal of American Statistical Association, DOI: 10.1080/01621459.2020.1811098.
	
	\item Cottrill, A.A., \textbf{Fulcher, I.R.}, Goldberg, A.B., Sabino, J., Fortin, J., \& Janiak, E. (2020) Time trends in Massachusetss adolescents' post-abortion contraceptive uptake. Journal of Adolescent Health. 
	
	\item Rindos, N.B., \textbf{Fulcher, I. R.}, \& Donellan, N.M. (2020). Pain and quality of life following laparoscopic excision of endometriosis. The Journal of Minimally Invasive Gynecology. DOI: 10.1016/j.jmig.2020.03.013
	
	\item Janiak, E., \textbf{Fulcher, I. R.}, ..., \& Goldberg, A. (2019). Impact of Massachusetts' parental involvement law on procedural timing among adolescents seeking abortion. Obstetrics \& Gynecology, 133(5): 978-986.
	
	\item Bao, E.L., Lareau, C. A., Brugnara, C., \textbf{Fulcher, I. R.} et al. (2019). Heritability of fetal hemoglobin, white cell count, and other clinical traits from a sickle cell disease family cohort. American Journal of Hematology. DOI: 10.1002/ajh.25421. 
	
\end{enumerate}


%% Honors and Awards
\section*{\textbf{{\large H}{ONORS} {\large \&} {\large A}{WARDS}}}
University of Florida Statistics Workshop Travel Award \hfill \hfill 2019 \\
National Science Foundation Travel Award for Atlantic Causal Inference Conference \hfill \hfill	2018 \\
Barry R. and Irene Tilenius Bloom Fellowship \hfill \hfill	2018 \\
Harvard University Distinction in Teaching \hfill \hfill 2017 \\
Harvard T.H. Chan School of Public Health Rose Traveling Fellowship \hfill \hfill	2017 \\
Maternal Health Task Force Travel Award \hfill \hfill	2017 \\
Statistics in Epidemiology Young Investigator Award  \hfill \hfill	2017 \\
McGill University Dean's Honour List  \hfill \hfill	2012 \\
Golden Key International Honour Society  \hfill \hfill2010, 2011, 2012 

%\section*{\textbf{{\large G}{RANTS} {\large \&} {\large F}{ELLOWSHIPS}}}

% Presentations
\section*{\textbf{{\large I}{NVITED} {\large T}{ALKS}}}   

%``Identification and estimation of indirect effects robust to unmeasured confounding" Society for Epidemiological Research, Boston, MA (December 2020). \\

``Supporting data-driven COVID-19 responses in low and middle income countries.'' Coronavirus Visualization Team, Online (August 2020). \\

``Estimation of natural indirect effects robust to unmeasured confounding and mediator measurement error.'' Joint Statistical Meetings, Online (August 2020). \\

``Bayesian auto-g-computation of network causal effects: incarceration and infection in a high risk network.'' ENAR, Online (March 2020). \\

``Auto-g-computation of network causal effects: incarceration and infection in a high risk network.'' Statistics Seminar, University of Rhode Island, Kingston, RI (March 2020). \\

``Bayesian auto-g-computation of network causal effects: incarceration and infection in a high risk network.'' Statistics \& Probability Seminar, University of Massachusetts Amherst, Amherst, MA (December 2019). \\

``Improving the delivery of healthcare to pregnant women in sub-Saharan Africa with statistics and data science.'' Mathematics and Statistics Colloquium, Colby College, Waterville, ME (December 2019). \\ 

``Bayesian auto-g-computation of network causal effects: incarceration and infection in a high risk network.'' Joint Statistical Meetings, Denver, CO (July 2019). \\

``Bayesian auto-g-computation of network causal effects: incarceration and infection in a high risk network.'' New England Statistical Society, Hartford, CT (May 2019). 

\section*{\textbf{{\large C}{ONFERENCE} {\large P}{ARTICIPATION}}}  

\subsection*{\textbf{CONTRIBUTED TALKS}}

% JSM 

``The generalized front-door formula for estimation of indirect causal effects of a confounded treatment.'' ENAR Spring Meeting, Atlanta, GA (2018). \\

``Data for decision-making in digital health programs: how analysis of routine data from the Safer Deliveries program in Zanzibar improved program implementation and mothers' outcomes.'' Global Digital Health Forum, Washington, DC (2017). \\

``Mediation analysis for censored survival data under an accelerated failure time model.'' Joint Statistical Meetings, Baltimore, MD (2017). \\

``The generalized front-door formula for identification of partial causal effects.'' ENAR Spring Meeting, Washington, DC (2017). \\

``Mediation analysis for censored survival data under an accelerated failure time model.'' ENAR Spring Meeting, Austin, TX (2016). 

\subsection*{\textbf{ POSTERS}}

``Bayesian auto-g-computation of network causal effects: incarceration and infection in a high risk network.'' 21st Meeting of New Researchers in 
Statistics and Probability. Fort Collins, CO (2019). \\

``Estimation of natural indirect effects robust to unmeasured confounding and mediator measurement error.'' University of Florida Winter Workshop, Gainesville, FL (2019). \\

``Nonparametric identification and robust estimation of indirect causal effects in the presence of exposure-outcome confounding.'' Atlantic Causal Inference Conference, Pittsburgh, PA (2018). \\

``Auto-g-computation of causal effects on a sexual and injection-drug use network.'' Harvard Data Science Conference, Cambridge, MA (2018). \\

``Working towards safer deliveries in Zanzibar, Tanzania.'' Future Health Campaign Celebration, Harvard T.H. Chan School of Public Health, Boston, MA (2018). \\

``Nonparametric identification and robust estimation of indirect causal effects in the presence of exposure-outcome confounding.'' Atlantic Causal Inference Conference, Pittsburgh, PA (2018). 

%\section*{\textbf{{\large C}{AMPUS} {\large T}{ALKS}}}  


%% Teaching Experience
\section*{\textbf{{\large T}{EACHING} {\large E}{XPERIENCE}}}
\textbf{Global Initiative for Neuropsychiatric Genetics Education in Research \hfill \hfill Addis Ababa, Ethiopia} \\
\textit{Teaching Fellow}, Interactive Biostatistics Workshop \hfill \hfill November 2019 \\

\textbf{Harvard T.H. Chan School of Public Health \hfill \hfill Boston, MA} \\
\textit{Instructor}, Biostatistics Preparatory Course: Methods and Computing in R \hfill \hfill Summer 2018 \\
\textit{Instructor}, Stata Orientation for Incoming Graduate Students \hfill \hfill	Summer 2016, 2017, 2018\\
\textit{Head Teaching Assistant}, Core Principles of Biostatistics and Epidemiology \hfill \hfill Fall 2016, 2017 \\
\textit{Teaching Assistant}, Core Principles of Biostatistics and Epidemiology \hfill \hfill Fall 2015 \\
\textit{Teaching Assistant}, Quantitative Methods in Program Evaluation \hfill \hfill Spring 2017 \\
\textit{Teaching Assistant}, Methods for Monitoring and Evaluation \hfill \hfill Spring 2016 \\

\textbf{University of Global Health Equity \hfill \hfill Kigali, Rwanda} \\
\textit{Teaching Assistant}, Program Monitoring, Evaluation, and Research Methods  \hfill \hfill Spring 2017, 2018 \\

\textbf{D-tree International \hfill \hfill Zanzibar, Tanzania}\\
\textit{Instructor}, Data Analysis and Stata Software Training Course \hfill \hfill Summer 2017  \\

\textbf{McGill University \hfill \hfill Montreal, QC}\\
\textit{Teaching Assistant}, Probability \hfill \hfill Fall 2010, 2011 \\
\textit{Teaching Assistant}, Statistics \hfill \hfill Spring 2012 

%\section*{\textbf{{\large A}{CADEMIC} {\large C}{ONSULTING} {\large E}{XPERIENCE}}}
%Bridge to Health USA \hfill \hfill May 2019 -- Present  \\
%Planned Parenthood League of Massachusetts \hfill \hfill August 2017 -- Present  \\
%D-tree International, Tanzania \hfill \hfill May 2017 -- Present \\
%Department of OB/GYN/RS, University of Pittsburgh School of Medicine  \hfill \hfill April 2018 -- March 2019 
%
%\section*{\textbf{{\large I}{NDUSTRY} {\large E}{XPERIENCE}}}
%\textbf{ZS Associates \hfill \hfill Evanston, IL} \\
%\textit{Business Associate} \hfill \hfill September 2012 -- July 2014 

\section*{\textbf{{\large P}{ROFESSIONAL} {\large S}{ERVICE}}}
\subsection*{\textbf{JOURNAL PEER REVIEWER}}
\textit{Annals of Global Health} \\ 
\textit{BMJ Open} \\ 
\textit{Biometrics} \\
\textit{Epidemiology} \\
\textit{Journal of Causal Inference} \\ 
\textit{Statistical Methods in Medical Research}

\subsection*{\textbf{UNIVERSITY ACTIVITY}}
\textit{Mentor}, Pipelines into Biostatistics Summer Program, Harvard T.H. Chan School of
Public Health \hfill \hfill 2018 \\
\textit{Student Committee Chair}, Department of Biostatistics, Harvard T.H. Chan School of
Public Health \hfill \hfill 2018 \\
\textit{Organizer}, HIV Working Group, Department of Biostatistics, Harvard T.H. Chan School of
Public Health \hfill \hfill 2017 



\end{document}